Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2024-12-30 ms.qmd
Few of R2 comments dealt with

A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers. `r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers. `r utils::packageVersion("ggtree")`) [@Yu2017-wj]. We resolved all polytomies in the tree. Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr]. Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$. As such, we used an intermediate value of p = 0.7. We used the R packages *ape* (vers. `r utils::packageVersion("ape")`) [@Paradis2019-gx] and *phytools* (vers. `r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.

@@

Finally, we tested whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (details on climate data can be found in the *Supplementary Materials*). We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses; though there were no differences between $lnVR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acute}}}$. We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5"). We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location. However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa. As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.

>>>>

A phylogeny was derived using the Open Tree of Life (OTL) with the *rotl* package in R (vers. `r utils::packageVersion("rotl")`) [@Michonneau2016-if], and plotted using *ggtree* (vers. `r utils::packageVersion("ggtree")`) [@Yu2017-wj]. We resolved all polytomies in the tree randomly using using the *multi2di* function in *ape* (vers. `r utils::packageVersion("ape")`) [@Paradis2019-gx]. Any missing taxa were replaced with closely related species and branch lengths were computed using Grafen's method [using power = 0.7, @Grafen1989-pr]. Models fit using correlation matrices computed with different power (p) parameters (from 0.5 – 1.0) had nearly identical $AIC_{c}$. As such, we used an intermediate value of p = 0.7. We used the R packages *ape*  and *phytools* (vers. `r utils::packageVersion("phytools")`) [@Revell2012-vq] to prune the tree for individual analyses and calculate phylogenetic covariance (or correlation) matrices used in meta-analytic models.

@@

Finally, we used the ERA5 climate model [@Hersbach2020-hx] to test whether the change in $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10}}$ were predicted by climate variability (CV) (see further details in the *Supplementary Materials*). We only used $lnRR_{Q_{10_{acclimation}}}$ and $lnVR_{Q_{10_{acclimation}}}$ for these models because our predictions were specifically focused on acclimation responses. We fit models that included an interaction between habitat type and thermal coefficient of variability (CV) as moderators (referred to as "Model 5"). We also explored whether environmental predictability explained capacity for acclimation; we estimated predictability as the correlation of temperatures across months at a given location. However, such analyses are challenging to interpret because the temporal scale that is biologically relevant to different organisms will be different making the choice of lag to estimate the correlation difficult to apply across taxa. As such, we report a simple analysis in the *Supplementary Materials* but note that it does not differ from our CV analysis.
